### 2021-10-29 NSF2021/Description/broaderimpacts.tex
incorporated Carolyn's changes

This project aims to advance the mathematical modeling of collective 
dynamics of amphiphilic particles. The simulations use a new, yet intuitive,
approach that can account for important and complex systems that are out of 
reach in computational material science. These complex systems include 
fusion and fission of amphiphilic bilayer membranes and optimal shape design
in metamaterials. The development of three-dimensional 
models describing colloidal systems could be transformative in biomedicine
and material science. The research draws from expertise in scientific 
computing, physics of fluids, and mathematics. The mathematical component 
incorporates leading techniques from geometric analysis and gives deep insight 
into fundamental material science. The project offers undergraduates 
in a socially impactful manner the opportunity to do research and train 
with graduate and postdoctoral personnel. It incorporates research in the 
classroom, and with its combination of mathematical modeling, analysis, 
and scientific computing, the project highlights the importance of 
mathematics and computation to all areas of science and engineering.

%The proposed mathematical analysis, modeling, and numerical algorithms
%will transform our understanding of the collective dynamics of
%amphiphilic particles such as (1) their self-assembly into micelles and
%bilayers, (2) the material properties of such self-assembly, and (3) the
%interaction between these building blocks. In addition to biophysical
%applications, amphiphilic Janus particles have recent popularity in the
%fabrication of smart materials. The proposed work will have a
%transformative impact on precision design for specific mechanical
%properties of materials made of amphiphilic nanoparticles. An important
%component of this proposal is the interdisciplinary education and
%training of both undergraduate students, graduate students, and
%postdoctoral fellows. The combination of mathematical modeling,
%analysis, and scientific computing in this project provides a compelling
%example of the importance of mathematics and computation in biophysics
%and engineering applications. The concepts and methods described here go
%beyond the context of amphiphilic particles and lipid molecules. They
%extend to other problems featuring microscopic phase separation that
%leads to formation of mesoscopic domains. This situation arises, for
%example, in biological development in systems biology. The methods
%developed here have the potential to impact those and other related
%areas in biomedicine and biotechnology.

@@

The URs will work as a team for eight weeks in the summer. They will
collaborate directly with the senior personnel, have tutorials in topics
such as numerical quadrature and integral equations, and train in
mathematical writing and presentation. To maximize vertical integration,
and to the extent possible, the PIs and personnel will travel to New
York for one or two weeks in the summers. Fordham University recently
constructed a seminar/collaboration space specifically for collaborative
research, and the URs will have office space with desks there.

As a requirement, the URs will write quality summary reports and give
presentations at the their respective research symposia. The work will
be considered a success if the URs also participate in a national
conference. The best possible outcome is if URs coauthor a publication.

>>>>

This project aims to advance the mathematical modeling of collective 
dynamics of amphiphilic particles. The simulations use a new, yet intuitive,
approach that can account for important and complex systems that are out of 
reach in computational material science. These complex systems include 
fusion and fission of amphiphilic bilayer membranes and optimal shape design
in metamaterials. The development of three-dimensional 
models describing colloidal systems could be transformative in biomedicine
and material science. The research draws from expertise in scientific 
computing, physics of fluids, and mathematics. The mathematical component 
incorporates leading techniques from geometric analysis and offers  
insight 
into fundamentals of material science. The project brings socially consequential research into the classroom, and offers undergraduates the opportunity to train alongside graduate students and postdoctoral fellows.  With its combination of mathematical modeling, analysis, and scientific computing, the project highlights the importance of mathematics and computation to all areas of science and engineering.
%The proposed mathematical analysis, modeling, and numerical algorithms
%will transform our understanding of the collective dynamics of
%amphiphilic particles such as (1) their self-assembly into micelles and
%bilayers, (2) the material properties of such self-assembly, and (3) the
%interaction between these building blocks. In addition to biophysical
%applications, amphiphilic Janus particles have recent popularity in the
%fabrication of smart materials. The proposed work will have a
%transformative impact on precision design for specific mechanical
%properties of materials made of amphiphilic nanoparticles. An important
%component of this proposal is the interdisciplinary education and
%training of both undergraduate students, graduate students, and
%postdoctoral fellows. The combination of mathematical modeling,
%analysis, and scientific computing in this project provides a compelling
%example of the importance of mathematics and computation in biophysics
%and engineering applications. The concepts and methods described here go
%beyond the context of amphiphilic particles and lipid molecules. They
%extend to other problems featuring microscopic phase separation that
%leads to formation of mesoscopic domains. This situation arises, for
%example, in biological development in systems biology. The methods
%developed here have the potential to impact those and other related
%areas in biomedicine and biotechnology.

@@

The URs will work as a team for eight weeks in the summer. They will
collaborate directly with the senior personnel, have tutorials in topics
such as numerical quadrature and integral equations, and train in
mathematical writing and presentation. To maximize vertical integration,
and to the extent possible, the PIs and personnel will travel to New
York for one or two weeks during the summers. Fordham University
recently constructed a seminar/collaboration space specifically for
collaborative research, and the URs will have office space with desks
there. As a requirement, the URs will write quality summary reports and
give presentations at the their respective research symposia. The work
will be considered successful if the URs also participate in a national
conference. In the best possible outcome, the URs will co-author a
publication.

### 2021-10-29 NSF2021/Description/priorsupport.tex
incorporated Carolyn's changes

\textbf{Collaboration plan}: 
%
The management responsibility of this collaborative research will reside
with the lead PI (Ryham) for this endeavor. The research work is
structured to meet the tasks discussed in \S\ref{sec:proposed-work}.
%
The PIs, their postdocs, and students will meet frequently on Zoom and
in person when possible. The PIs will share software packages, paper
sources, and references on a common \textsf{Git} repository. The
resulting software packages will be posted on the \textsf{Github}
software repository.

>>>>

\textbf{Collaboration plan}: 
%
The management responsibility of this collaborative research will reside
with the lead PI (Ryham) for this endeavor. The research work is
structured to meet the tasks discussed in \S\ref{sec:proposed-work}.
%
The PIs, postdocs, and students will meet frequently on Zoom and
in person when possible. During the pandemic, the three PIs will meet
weekly on Zoom for a research meeting. Once the pandemic is under control, PI RR and PI YNY will conduct biweekly meetings in person, with PI BQ Zoom in from Florida.
The PIs will share software packages, paper
sources, and references on a common \textsf{Git} repository. The
resulting software packages will be posted on the \textsf{Github}
software repository.

### 2021-10-29 NSF2021/Description/specificaim3.tex
incorporated Carolyn's changes

\subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
In recent experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending
rigidity was determined as a function of lipid composition from 0 to 100
mol $\%$ of charged lipids using flicker spectroscopy of the shape
fluctuations of a giant unilamellar vesicle (GUV).
%the bending rigidity is determined as a
%function of lipid composition from 0 to 100 mol $\%$ of charged lipids
%in recent experiments~\cite{FaizEtAl2019_SoftMatt}---
Membrane bending rigidity increases with increasing lipid surface
charge, while decreases with increasing salt concentration in the bulk
solution due to the screening of the lipid surface charge. This agrees
with several theoretical models~\cite{Kralchevsky1996_JCIS,
May1996_JChemPhys, LoubetEtAl2013_PRE} that also assume the quadratic
form of the elastic energy density in the presence of surface charge and
bulk charge~\cite{DuplantierGoldstein1990_PRL, Winterhalter1992_JPC}. As
the electrostatic interaction is non-local in nature, we expect that the
controversy of the HK elastic energy form (see
\S\ref{subsec:specific_aim_1}) would worsen in the presence of
electrostatic interactions and electrokinetics. The PIs will extend the
approaches in \S\ref{subsec:specific_aim_1} to charged lipids to
calculate the bending moduli and compare against the experimental
results in~\cite{FaizEtAl2019_SoftMatt}. We propose to incorporate an
explicit surface charge on each particle boundary $P_i$ and compute the
electrostatic potential as a functional of particle configuration.
Adding the electrostatic force to the hydrophobic attraction force
between particles, we will assess the dependence of elastic moduli on
electric charges using the methods described in
\S\ref{subsec:specific_aim_1}. Results from these proposed calculations
will provide further comparisons and validations of the HAP model
against the continuum mechanics.

>>>>

\subsubsection{Electromechanical effects on the dynamic assembly of amphiphiles \label{subsubsec:em_effects}}
In recent experiments~\cite{FaizEtAl2019_SoftMatt}, membrane bending
rigidity was determined as a function of lipid composition from 0 to 100
mol $\%$ of charged lipids using flicker spectroscopy of the shape
fluctuations of a giant unilamellar vesicle (GUV).
%the bending rigidity is determined as a
%function of lipid composition from 0 to 100 mol $\%$ of charged lipids
%in recent experiments~\cite{FaizEtAl2019_SoftMatt}---
Membrane bending rigidity increases with increasing lipid surface
charge, but decreases with increasing salt concentration in the bulk
solution due to the screening of the lipid surface charge. This
result agrees
with several theoretical models~\cite{Kralchevsky1996_JCIS,
May1996_JChemPhys, LoubetEtAl2013_PRE} that also assume the quadratic
form of the elastic energy density in the presence of surface charge and
bulk charge~\cite{DuplantierGoldstein1990_PRL, Winterhalter1992_JPC}. As
the electrostatic interaction is non-local in nature, we expect that the
controversy of the HK elastic energy form (see
\S\ref{subsec:specific_aim_1}) would worsen in the presence of
electrostatic interactions and electrokinetics. The PIs will extend the
approaches in \S\ref{subsec:specific_aim_1} to charged lipids to
calculate the bending moduli and compare against the experimental
results in~\cite{FaizEtAl2019_SoftMatt}. We propose to incorporate an
explicit surface charge on each particle boundary $P_i$ and compute the
electrostatic potential as a functional of particle configuration.
Adding the electrostatic force to the hydrophobic attraction force
between particles, we will assess the dependence of elastic moduli on
electric charges using the methods described in
\S\ref{subsec:specific_aim_1}. Results from these proposed calculations
will provide further comparisons and validations of the HAP model
against the continuum mechanics.
